---
title: "'Introduction to ggplot2' seminar"
output:
  github_document: default
  html_notebook: default
---

```{r}
library(tidyverse)
```

Graham Parsons - Data Scientist

```{r}
View(diamonds)
```

```{r}
myPlot <- qplot(x = carat, y = price, data = diamonds)
```

```{r}
qplot(carat, data = diamonds, bins = 10,
      main = "Carat Histogram", xlab = "Carat", ylab = "Count")
```

```{r}
View(mtcars)
```

```{r}
qplot(wt, mpg, data = mtcars, ylim = c(0, NA)) # NA means let qplot decide the upper limit
```

Exercise 1

```{r}
pkData <- read_csv("pkData.csv")
demoData <- read_csv("demoData.csv")
```

Exercise 1.1
Create a plot of Conc against Time from pkData (in theMangoTraining package)
```{r}
qplot(x= Time, y = Conc, data = pkData,
      main = "Concentration v's Time",
      xlab = "Time", ylab = "Conc")
```

Exercise 1.2
Ensure that the Conc axis ranges from 0 to 2500
```{r}
```{r}
qplot(x = Time, y = Conc, data = pkData,
      main = "Concentration v's Time",
      xlab = "Time", ylab = "Conc",
      ylim = c(0, 2500))
```

Exercise 1.3
Create a histogram of weight from demoData
```{r}
myHist <- qplot(x = Weight, data = demoData, binwidth = 2)
ggsave("myPlot.png", plot = myHist)
```

```{r}
qplot(mpg, hp, data = mtcars) +
  lims(x = c(0, 90), y = c(0, 400)) +
  labs(x = "Miles per Gallon", y = "Horsepower") +
  ggtitle("My Plot")
```

```{r}
qplot(factor(cyl), mpg, data = mtcars, geom = "boxplot")
```

```{r}
qplot(mpg, wt, data = mtcars) +
  geom_smooth(method = "loess")
```


EXERCISES 2

Exercise 2.1
Create a boxplot of Height against Sex from `demoData`

```{r}
qplot(x = Sex, y = Height, data = demoData, geom = "boxplot")
```

Exercise 2.2
Generate some random numbers using `rnorm()` and draw a simple density plot to display the data

```{r}
random <- rnorm(100)
qplot(x = random, geom = "density")
```

Exercise 2.3
Create a plot of Conc against Time from pkData
```{r}
qplot(x = Time, y = Conc, data = pkData)
```

Exercise 2.4
Add a smoothing line to the plot
```{r}
qplot(x = Time, y = Conc, data = pkData) +
  geom_smooth()
```

Exercise 2.5
Change the smoothing function in the previous exercise to a linear (`lm`) smoother (not statistically sensible) and remove the error bars

```{r}
qplot(x = Time, y = Conc, data = pkData) +
  geom_smooth(method = "lm", se = FALSE)
```

---

Aesthetics and Groups

```{r}
View(quakes)
```

```{r}
qplot(x = long, y = lat, data = quakes, size = mag, colour = -depth)
```

```{r}
qplot(mpg, wt, data = mtcars, colour = factor(cyl))
```

```{r}
qplot(mpg, wt, data = mtcars, colour = "blue")
qplot(mpg, wt, data = mtcars, colour = I("blue"))
```

If you don't like the actual colours used :

```{r}
qplot(mpg, wt, data = mtcars, colour = factor(cyl)) +
  scale_colour_manual(values = c("hotpink", "red", "navy"))

qplot(mpg, wt, data = mtcars, colour = factor(cyl)) +
  scale_colour_brewer(type = "qual", "Dark2") # ??? dark2 didn't work?
```


EXERCISES 3

Exercise 3.1
Create a scatter plot of Height against Weight using demoData. Use a different colour to distinguish between males and females and a different plotting symbol dependent upon whether the subject smokes or not

```{r}
qplot(x = Weight, y = Height, data = demoData, colour = Sex, shape = Smokes)
```


Exercise 3.2
Increase the size of the points on the previous plot to twice the default size
```{r}
qplot(x = Weight, y = Height, data = demoData, colour = Sex, shape = Smokes, size = I(2))
```

---

Advanced Control of Aesthetics

```{r}
qplot(x = long, y = lat, data = quakes, size = mag, col = -depth, alpha = I(0.2)) +
  scale_colour_continuous("Depth", low = "darkred", high = "yellow")
```

```{r}
qplot(Time, Conc, data = pkData, geom = "line", group = Subject)

qplot(Time, Conc, data = pkData, geom = "line", col = factor(Subject))
```

```{r}
qplot(carat, price, data = diamonds, alpha = I(0.2)) +
  facet_grid(. ~ cut)

qplot(carat, price, data = diamonds, alpha = I(0.2)) +
  geom_smooth() +
  facet_grid(color ~ cut)
```


EXERCISES 4

Exercise 4.1
Draw a "line" plot of Conc against Time from pkData and colour by Dose

```{r}
qplot(x = Time, y = Conc, data = pkData, geom = "line", group = Subject, colour = Dose)

qplot(x = Time, y = Conc, data = pkData, geom = "line", group = Subject, colour = factor(Dose))
```

Exercise 4.2
Change the previous plot so that each level of Dose is instead represented by a separate panel

```{r}
qplot(x = Time, y = Conc, data = pkData, geom = "line", group = Subject) +
  facet_grid(. ~ Dose)
```


Exercise 4.3
Draw a "line" plot of Conc against Time from pkData. Ensure each Subject is drawn in a different panel and vary the line type by Dose

```{r}
qplot(x = Time, y = Conc, data = pkData, geom = "line", linetype = factor(Dose)) +
  facet_wrap(~Subject, nrow = 6)
```

Exercise 4.4
Create a plot of Height against Weight from demoData. Panel (facet) the plot to show levels of Sex in the rows and Smokes in the columns

```{r}
qplot(x = Weight, y = Height, data = demoData) +
  facet_grid(Sex ~ Smokes)
```


---

```{r}
qplot(mpg, wt, data = mtcars, col = factor(cyl), size = I(2))

ggplot(mtcars, aes(x = mpg, y = wt, col = factor(cyl))) +
  geom_point(size = 2)
```


ggplot gallery : Top 50 visualizations

